Stepwise Multiple Regressions

### 2021-02-03 Stepwise Multiple Regressions.Rmd
Added headings for clairty

#Convert all data to numerical data
aoc_setup_selected_num <- data.matrix(aoc_setup_selected)

@@

summary(Full_Model)

@@

summary(Full_Model)

>>>>

### Full

```{r, echo = FALSE}
#Convert all data to numerical data
aoc_setup_selected_num <- data.matrix(aoc_setup_selected)

@@

summary(Full_Model)
```

### Stepwise

```{r, echo = FALSE}
#Stepwise model
step.model <- stepAIC(Full_Model, direction = "both", 
                      trace = FALSE)

@@

#Fit the full model
Full_Model <- lm(effect ~., data = y)
```

### Stepwise

```{r, echo = FALSE}
summary(Full_Model)
